---
title: "rmarkdown notes"
author: "Steven Wong"
output: pdf_document
---

# Install

# Resources

[RStudio R Markdown][1]  
[R Markdown Cheat Sheet][2]  
[R Markdown Reference Guide][3]
[Bookdown: Books with R Markdown][4]

[1]: http://rmarkdown.rstudio.com/
[2]: https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
[3]: https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf
[4]: https://bookdown.org/yihui/bookdown/

# Basics

A YAML is header is a set of key. Output can also be:  

* pdf_document
* word_document
* beamer_document
* ioslides_document

To knitr the .Rmd file to the output, in R, execute:
```{r eval=F}
render("file.rmd")
```

To knitr the .Rmd file as `shiny` output, in R, execute:
```{r eval=F}
run("file.rmd")
```

***

# Basic Syntax

Plain text  
End a line with two spaces
to start a new paragraph.  

Or\
End a line with a `\`. This is useful in tables.

Put an empty line between two line 
to start a new paragraph, with a gap.

*italics* and _italics_  
**bold** and __bold__  
superscript^2^  
~~strikethrough~~  
[link](www.rstudio.com)  

Header 1
========

Header 2
--------

# Header 1  

## Header 2  

### Header 3

#### Header 4

##### Header 5

###### Header 6

endash: --  
emdash: ---  
ellipsis: ...  
inline equation: $A = \pi*r^{2}$  

> block quote

```
plain code blocks
```

Inline `code block`. 

LaTeX Equations:  
Inline: $equation$  
Display equation: $$ equation $$

* unordered list
* item 2
	+ sub-item 1
	+ sub-item 2

1. ordered list
2. item 2
	+ sub-item 1
	+ sub-item 2

Table Header | Second Header
------------ | -------------
Table Cell   | Cell 2
Cell 3       | Cell 4 

horizontal rule (or slide break; 3 or more is good):  

---
***

# Embedding R Codes

Default:
```{r}
paste("Hello, World!")
```

Include code: 2 + 2 = `r 2+2`

#### Chuck Options (inside {r})

To only show the codes:
```{r eval=F}
paste("Hello, World!")
```
To only show the evaluation:
```{r echo=F}
paste("Hello, World!")
```
#### Example: 
```{r echo=F, message=F}
library(dplyr)
library(ggplot2)
library(shiny)
library(rmarkdown)
library(readr)
```

With ggplot2:
```{r fig.height=2.5, fig.width=5, fig.align='center'}
imdb <- read_csv('~/Documents/Projects/IMDB/ratings_list_short_151120.csv')
ggplot(imdb, aes(x = Rating)) + 
  geom_histogram(binwidth = 0.2)
```
